Binning Strategies and Related Loss for Large Data

### 2015-04-07 Paper.Rnw
Add frequency loss comparison plot for standard and quantile frequency binning.

<<ExponentialOriginPlots, echo=F,include=T,eval=T,fig.width=8, fig.height=3, out.width='.9\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Binned scatterplots for the fine exponential data using standard binning with 10 by 10 unit bins with origins at (0,0) and (-9,-9). These binnings have net spatial losses of 391067 units and 420458 units, respectively">>=

@@

>>>>

<<ExponentialOriginPlots, echo=F,include=T,eval=T,fig.width=8, fig.height=3, out.width='.9\\linewidth', fig.pos='H',fig.align='center',tidy=F, cache=TRUE, fig.show='hold',fig.cap="Binned scatterplots for the fine exponential data using standard binning with 10 by 10 unit bins with origins at (0,0) and (-9,-9). These binnings have net spatial losses of 391067 units and 420458 units, respectively">>=

@@

<<FreqLossCompare,echo=F,include=T,eval=T,fig.width=10, fig.height=4, out.width='.99\\linewidth', fig.pos='H',fig.align='center',tidy=F, cache=TRUE, warning=F, fig.show='hold',fig.cap="Lineplots for total frequency loss from standard and quantile frequency binning of reduced binned data from each bivariate distribution. Spatial binning to produce the reduced binned data done with standard rectangular binning with 5 X 5 unit bins and origin at (0,0).">>= 
### Loop over ncolors 1 to 7 and also over data distribution
# find freq loss from standard, quantile, logCount
freqLossSimDat <- NULL
distrib <- c("Uniform", "Normal", "Exponential")
for (distidx in 1:3){
  binout1 <- RectBin2d(datlist[[distidx]]$x,datlist[[distidx]]$y,0,0,5,5,type="standard")
  for (ncol in 1:7){
    binoutFreq <- rbind(freqBin(binout1, binType="standard", ncolor=ncol, logCount=FALSE)[[2]],
                        freqBin(binout1, binType="quantile", ncolor=ncol, logCount=FALSE)[[2]], 
                        freqBin(binout1, binType="standard", ncolor=ncol, logCount=TRUE)[[2]])
    binoutFreq$FreqBinType <- c("Standard", "Quantile", "Log Count")
    binoutFreq$DistType <- distrib[distidx]
    binoutFreq$ncolor <- ncol 
    freqLossSimDat <- rbind(freqLossSimDat,binoutFreq)
  }
}

freqLossSimDat$FreqBinType <- factor(freqLossSimDat$FreqBinType , levels=c("Standard", "Quantile", "Log Count"))
plotdat <- freqLossSimDat[(freqLossSimDat$FreqBinType!="Log Count" & freqLossSimDat$DistType=="Exponential"),]
p1 <- qplot(ncolor, totalFreqLoss, geom="path",linetype=FreqBinType,
      data=plotdat , color = FreqBinType, size=I(1)) +
  facet_grid(.~DistType, scales="free_y") +  theme_bw() +
  scale_x_continuous(breaks=c(1,3,5,7)) + ylim(0,max(plotdat$totalFreqLoss)) +
  xlab("Freq Bins") + ylab("Total Freq Loss") + 
  theme(legend.position="bottom")
plotdat <- freqLossSimDat[(freqLossSimDat$FreqBinType!="Log Count" & freqLossSimDat$DistType=="Normal"),]
p2 <-  qplot(ncolor, totalFreqLoss, geom="path",linetype=FreqBinType,
      data=plotdat , color = FreqBinType, size=I(1)) +
  facet_grid(.~DistType, scales="free_y") +  theme_bw() +
  scale_x_continuous(breaks=c(1,3,5,7)) + ylim(0,max(plotdat$totalFreqLoss)) +
  xlab("Freq Bins") + ylab("Total Freq Loss") + 
  theme(legend.position="bottom")
plotdat <- freqLossSimDat[(freqLossSimDat$FreqBinType!="Log Count" & freqLossSimDat$DistType=="Uniform"),]
p3 <-qplot(ncolor, totalFreqLoss, geom="path",linetype=FreqBinType,
      data=plotdat , color = FreqBinType, size=I(1)) +
  facet_grid(.~DistType, scales="free_y") +  theme_bw() +
  scale_x_continuous(breaks=c(1,3,5,7)) + ylim(0,max(plotdat$totalFreqLoss)) +
  xlab("Freq Bins") + ylab("Total Freq Loss") + 
  theme(legend.position="bottom")

grid.arrange(p1,p2,p3, nrow=1)
@
